---
title: "exp preference"
author: "Allen Yeh"
output:
  html_document: default
  pdf_document: default
---

```
```

```{r warning=FALSE}
library(tidyverse)
library(gmodels)
library(rstatix)
library(ggplot2)
library(ez)
library(ARTool)
library(emmeans)
```

### Import data

#### Read the csv file and claim the data type
```{r}
category_level <- c("easiness", "comfort", "confidence", "social")

participants <- read_csv("participants-short.csv", col_types = cols(
  id = col_integer(),
  gender = col_factor(levels = c("Male","Female")), 
  age = col_integer(), 
  handed = col_factor(levels = c("Right","Left")), 
  phoneExperience = col_factor(levels = c("-3","3-5", "6-10", "10-")),
  phoneSize = col_factor(levels = c("-4", "4-5", "5-6", "6-")), 
  dailyUsage = col_factor(levels = c("-1", "1-2", "2-4", "4-8", "8-")), 
  handLength = col_double(),
  handWidth = col_double()
)) %>%
  mutate(
    phoneSize_Num = phoneSize  %>%  recode(
          "-4" = 1,
          "4-5" = 2,
          "5-6" = 3,
          "6-" = 4
          )
      )

lefthanded_ids <- c(14, 11)


data <- read_csv("summaryPreference.csv", col_types = cols(
  id = col_integer(),
  type = col_factor(levels = c("0", "1", "2")),
  direction = col_factor(levels = c("0", "1")), 
  angle = col_factor(levels = c("-1", "0", "1", "2")),
  location = col_integer(),
  category = col_factor(levels = category_level),
  rating = col_integer()
  )) %>%
  mutate(
    type_code = type %>% recode_factor(
      `2` = "FOLDTOUCH",  
      `1` = "TOUCHFOLD",
      `0` = "FOLD"
      ),
    direction_code = direction %>% recode_factor(
      `1` = "OUTWARD",
      `0` = "INWARD"
      ),
    angle_code = angle %>% recode_factor(
      `2` = "LARGE",
      `1` = "MEDIUM",
      `0` = "SMALL",
      `-1` = "NONE"
      ),
    locationX = ifelse(id %in% lefthanded_ids, (1 - location %% 2), (location %% 2)),
    locationX_code = locationX %>% recode_factor(
      `1` = "FAR",
      `0` = "NEAR"
      ),
    locationY = ceiling(location/2) - 1,
)


```




### Fold interaction

#### Ease
```{r warning=FALSE}

gesture_level <- c("INWARD_SMALL", "INWARD_MEDIUM", "INWARD_LARGE", "OUTWARD_SMALL", "OUTWARD_MEDIUM", "OUTWARD_LARGE")

fold_trials <- data %>%
  filter(type_code == "FOLD") %>%
  mutate(
    gesture_code = fct_relevel(paste(direction_code, angle_code, sep = "_"), 
            "INWARD_SMALL", "INWARD_MEDIUM", "INWARD_LARGE", "OUTWARD_SMALL", "OUTWARD_MEDIUM", "OUTWARD_LARGE"),
      )

fold_ease <- fold_trials %>%
  filter(category == "easiness")

participants_fold_ease <- full_join(fold_ease, participants)

boxplot(rating~gesture_code,data=fold_ease, main="Ease",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


fold_ease_summary <-fold_ease %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_ease_summary

# line + dot
ease_graph <- ggplot(fold_ease_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

ease_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("ease_fold.pdf", width = 4, height = 3)

# fold_ease_direction_summary <-fold_ease %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# ease_graph <- ggplot(fold_ease_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# ease_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("ease_fold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

fold_data_summary <-fold_ease %>%
  group_by(direction_code, angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_data_summary

fold_direction_summary <-fold_ease %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_direction_summary


fold_angle_summary <-fold_ease %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_angle_summary

shapiro.test(fold_ease$rating)

fold_ease$id = factor(fold_ease$id)

m <- art(
  rating ~ direction_code*angle_code + (1|id),
  data = fold_ease
)

anova(m)

art.con(m, "direction_code")
art.con(m, "angle_code")
art.con(m, "direction_code:angle_code")


```


#### Comfort
```{r warning=FALSE}


fold_comfort <- fold_trials %>%
  filter(category == "comfort")

participants_fold_comfort <- full_join(fold_comfort, participants)

boxplot(rating~gesture_code,data=fold_comfort, main="Comfort",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


fold_comfort_summary <-fold_comfort %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_comfort_summary

# line + dot
comfort_graph <- ggplot(fold_comfort_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

comfort_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("comfort_fold.pdf", width = 4, height = 3)

# fold_comfort_direction_summary <-fold_comfort %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# comfort_graph <- ggplot(fold_comfort_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# comfort_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("comfort_fold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

fold_data_summary <-fold_comfort %>%
  group_by(direction_code, angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_data_summary

fold_direction_summary <-fold_comfort %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_direction_summary


fold_angle_summary <-fold_comfort %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_angle_summary

shapiro.test(fold_comfort$rating)

fold_comfort$id = factor(fold_comfort$id)

m <- art(
  rating ~ direction_code*angle_code + (1|id),
  data = fold_comfort
)

anova(m)

art.con(m, "direction_code")
art.con(m, "angle_code")
art.con(m, "direction_code:angle_code")

```

#### Confidence
```{r warning=FALSE}


fold_confidence <- fold_trials %>%
  filter(category == "confidence")

participants_fold_confidence <- full_join(fold_confidence, participants)

boxplot(rating~gesture_code,data=fold_confidence, main="Confidence",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


fold_confidence_summary <-fold_confidence %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_confidence_summary

# line + dot
confidence_graph <- ggplot(fold_confidence_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#EB984E", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

confidence_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("confidence_fold.pdf", width = 4, height = 3)

# fold_confidence_direction_summary <-fold_confidence %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# confidence_graph <- ggplot(fold_confidence_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#c0392b", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# confidence_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("confidence_fold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

fold_data_summary <-fold_confidence %>%
  group_by(direction_code, angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_data_summary

fold_direction_summary <-fold_confidence %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_direction_summary


fold_angle_summary <-fold_confidence %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_angle_summary

shapiro.test(fold_confidence$rating)

fold_confidence$id = factor(fold_confidence$id)

m <- art(
  rating ~ direction_code*angle_code + (1|id),
  data = fold_confidence
)

anova(m)

art.con(m, "direction_code")
art.con(m, "angle_code")
art.con(m, "direction_code:angle_code")

```

#### Social acceptance
```{r warning=FALSE}


fold_social <- fold_trials %>%
  filter(category == "social")

participants_fold_social <- full_join(fold_social, participants)

boxplot(rating~gesture_code,data=fold_social, main="Social",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


fold_social_summary <-fold_social %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_social_summary

# line + dot
social_graph <- ggplot(fold_social_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#A569BD", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

social_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("social_fold.pdf", width = 4, height = 3)

# fold_social_direction_summary <-fold_social %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# social_graph <- ggplot(fold_social_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#5d6d7e", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# social_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("social_fold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

fold_data_summary <-fold_social %>%
  group_by(direction_code, angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_data_summary

fold_direction_summary <-fold_social %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_direction_summary


fold_angle_summary <-fold_social %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

fold_angle_summary

shapiro.test(fold_social$rating)

fold_social$id = factor(fold_social$id)

m <- art(
  rating ~ direction_code*angle_code + (1|id),
  data = fold_social
)

anova(m)

art.con(m, "direction_code")
art.con(m, "angle_code")
art.con(m, "direction_code:angle_code")

```


### Touch-enhanced Fold interaction

#### Ease
```{r warning=FALSE}

touchfold_trials <- data %>%
  filter(type_code == "TOUCHFOLD") %>%
  mutate(
    gesture_code = fct_relevel(paste(direction_code, locationX_code, locationY, sep = "_"), 
            "INWARD_FAR_0", "INWARD_NEAR_0", "INWARD_FAR_1", "INWARD_NEAR_1", "INWARD_FAR_2", "INWARD_NEAR_2", "INWARD_FAR_3", "INWARD_NEAR_3", "OUTWARD_FAR_0", "OUTWARD_NEAR_0", "OUTWARD_FAR_1", "OUTWARD_NEAR_1", "OUTWARD_FAR_2", "OUTWARD_NEAR_2", "OUTWARD_FAR_3", "OUTWARD_NEAR_3"),
      )

touchfold_ease <- touchfold_trials %>%
  filter(category == "easiness")


participants_touchfold_ease <- full_join(touchfold_ease, participants)

boxplot(rating~gesture_code,data=touchfold_ease, main="Ease",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


touchfold_ease_summary <-touchfold_ease %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_ease_summary

# line + dot
ease_graph <- ggplot(touchfold_ease_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

ease_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("ease_touchfold.pdf", width = 4, height = 8)

# touchfold_ease_direction_summary <-touchfold_ease %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# ease_graph <- ggplot(touchfold_ease_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# ease_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("ease_touchfold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

touchfold_data_summary <-touchfold_ease %>%
  group_by(direction_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_data_summary

touchfold_direction_summary <-touchfold_ease %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_summary


touchfold_X_summary <-touchfold_ease %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_X_summary

touchfold_Y_summary <-touchfold_ease %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_Y_summary

touchfold_direction_Y_summary <-touchfold_ease %>%
  group_by(direction_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_Y_summary

shapiro.test(touchfold_ease$rating)

touchfold_ease$id = factor(touchfold_ease$id)
touchfold_ease$locationY = factor(touchfold_ease$locationY)

m <- art(
  rating ~ direction_code*locationX_code*locationY + (1|id),
  data = touchfold_ease
)

anova(m)

art.con(m, "direction_code")
art.con(m, "locationY")
art.con(m, "direction_code:locationY")


```


#### Comfort
```{r warning=FALSE}


touchfold_comfort <- touchfold_trials %>%
  filter(category == "comfort")

participants_touchfold_comfort <- full_join(touchfold_comfort, participants)

boxplot(rating~gesture_code,data=touchfold_comfort, main="Comfort",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


touchfold_comfort_summary <-touchfold_comfort %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_comfort_summary

# line + dot
comfort_graph <- ggplot(touchfold_comfort_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

comfort_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("comfort_touchfold.pdf", width = 4, height = 8)

# touchfold_comfort_direction_summary <-touchfold_comfort %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# comfort_graph <- ggplot(touchfold_comfort_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# comfort_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("comfort_touchfold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

touchfold_data_summary <-touchfold_comfort %>%
  group_by(direction_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_data_summary

touchfold_direction_summary <-touchfold_comfort %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_summary


touchfold_X_summary <-touchfold_comfort %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_X_summary

touchfold_Y_summary <-touchfold_comfort %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_Y_summary

touchfold_direction_Y_summary <-touchfold_comfort %>%
  group_by(direction_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_Y_summary

shapiro.test(touchfold_comfort$rating)

touchfold_comfort$id = factor(touchfold_comfort$id)
touchfold_comfort$locationY = factor(touchfold_comfort$locationY)


m <- art(
  rating ~ direction_code*locationX_code*locationY + (1|id),
  data = touchfold_comfort
)

anova(m)

art.con(m, "direction_code")
art.con(m, "locationY")

art.con(m, "direction_code:locationY")
```

#### Confidence
```{r warning=FALSE}


touchfold_confidence <- touchfold_trials %>%
  filter(category == "confidence")

participants_touchfold_confidence <- full_join(touchfold_confidence, participants)

boxplot(rating~gesture_code,data=touchfold_confidence, main="Confidence",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


touchfold_confidence_summary <-touchfold_confidence %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_confidence_summary

# line + dot
confidence_graph <- ggplot(touchfold_confidence_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#EB984E", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

confidence_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("confidence_touchfold.pdf", width = 4, height = 8)

# touchfold_confidence_direction_summary <-touchfold_confidence %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# confidence_graph <- ggplot(touchfold_confidence_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#c0392b", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# confidence_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("confidence_touchfold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

touchfold_data_summary <-touchfold_confidence %>%
  group_by(direction_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_data_summary

touchfold_direction_summary <-touchfold_confidence %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_summary


touchfold_X_summary <-touchfold_confidence %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_X_summary

touchfold_Y_summary <-touchfold_confidence %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_Y_summary

shapiro.test(touchfold_confidence$rating)

touchfold_confidence$id = factor(touchfold_confidence$id)
touchfold_confidence$locationY = factor(touchfold_confidence$locationY)

m <- art(
  rating ~ direction_code*locationX_code*locationY + (1|id),
  data = touchfold_confidence
)

anova(m)

art.con(m, "direction_code")
art.con(m, "locationY")

```

#### Social acceptance
```{r warning=FALSE}


touchfold_social <- touchfold_trials %>%
  filter(category == "social")

participants_touchfold_social <- full_join(touchfold_social, participants)

boxplot(rating~gesture_code,data=touchfold_social, main="Social",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


touchfold_social_summary <-touchfold_social %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_social_summary

# line + dot
social_graph <- ggplot(touchfold_social_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#A569BD", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

social_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("social_touchfold.pdf", width = 4, height = 8)

# touchfold_social_direction_summary <-touchfold_social %>%
#   group_by(direction_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# social_graph <- ggplot(touchfold_social_direction_summary) +
#   geom_pointrange( aes(x=direction_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#5d6d7e", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# social_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("social_touchfold_direction.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

touchfold_data_summary <-touchfold_social %>%
  group_by(direction_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_data_summary

touchfold_direction_summary <-touchfold_social %>%
  group_by(direction_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_summary


touchfold_X_summary <-touchfold_social %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_X_summary

touchfold_Y_summary <-touchfold_social %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_Y_summary

touchfold_direction_Y_summary <-touchfold_social %>%
  group_by(direction_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

touchfold_direction_Y_summary

shapiro.test(touchfold_social$rating)

touchfold_social$id = factor(touchfold_social$id)
touchfold_social$locationY = factor(touchfold_social$locationY)

m <- art(
  rating ~ direction_code*locationX_code*locationY + (1|id),
  data = touchfold_social
)

anova(m)

art.con(m, "direction_code")
art.con(m, "locationY")
art.con(m, "direction_code:locationY")

```

### Fold-enhanced Touch interaction

#### Ease
```{r warning=FALSE}

foldtouch_trials <- data %>%
  filter(type_code == "FOLDTOUCH") %>%
  mutate(
    gesture_code = fct_relevel(paste(angle_code, locationX_code, locationY, sep = "_"), 
            "SMALL_FAR_1", "SMALL_NEAR_1", "SMALL_FAR_2", "SMALL_NEAR_2", "MEDIUM_FAR_1", "MEDIUM_NEAR_1", "MEDIUM_FAR_2", "MEDIUM_NEAR_2"),
      )

foldtouch_ease <- foldtouch_trials %>%
  filter(category == "easiness")

participants_foldtouch_ease <- full_join(foldtouch_ease, participants)

boxplot(rating~gesture_code,data=foldtouch_ease, main="Ease",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


foldtouch_ease_summary <-foldtouch_ease %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_ease_summary

# line + dot
ease_graph <- ggplot(foldtouch_ease_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

ease_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("ease_foldtouch.pdf", width = 4, height = 4)

# foldtouch_ease_angle_summary <-foldtouch_ease %>%
#   group_by(angle_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# ease_graph <- ggplot(foldtouch_ease_angle_summary) +
#   geom_pointrange( aes(x=angle_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# ease_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("ease_foldtouch_angle.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

foldtouch_data_summary <-foldtouch_ease %>%
  group_by(angle_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_data_summary

foldtouch_angle_summary <-foldtouch_ease %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_angle_summary


foldtouch_X_summary <-foldtouch_ease %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_X_summary

foldtouch_Y_summary <-foldtouch_ease %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_Y_summary

foldtouch_XY_summary <-foldtouch_ease %>%
  group_by(locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_XY_summary


shapiro.test(foldtouch_ease$rating)

foldtouch_ease$id = factor(foldtouch_ease$id)
foldtouch_ease$locationY = factor(foldtouch_ease$locationY)

m <- art(
  rating ~ angle_code*locationX_code*locationY + (1|id),
  data = foldtouch_ease
)

anova(m)

art.con(m, "locationX_code:locationY")
art.con(m, "locationY")


```


#### Comfort
```{r warning=FALSE}


foldtouch_comfort <- foldtouch_trials %>%
  filter(category == "comfort")

participants_foldtouch_comfort <- full_join(foldtouch_comfort, participants)

boxplot(rating~gesture_code,data=foldtouch_comfort, main="Comfort",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


foldtouch_comfort_summary <-foldtouch_comfort %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_comfort_summary

# line + dot
comfort_graph <- ggplot(foldtouch_comfort_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

comfort_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("comfort_foldtouch.pdf", width = 4, height = 4)

# foldtouch_comfort_angle_summary <-foldtouch_comfort %>%
#   group_by(angle_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# comfort_graph <- ggplot(foldtouch_comfort_angle_summary) +
#   geom_pointrange( aes(x=angle_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# comfort_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("comfort_foldtouch_angle.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

foldtouch_data_summary <-foldtouch_comfort %>%
  group_by(angle_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_data_summary

foldtouch_angle_summary <-foldtouch_comfort %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_angle_summary


foldtouch_X_summary <-foldtouch_comfort %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_X_summary

foldtouch_Y_summary <-foldtouch_comfort %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_Y_summary

foldtouch_XY_summary <-foldtouch_comfort %>%
  group_by(locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_XY_summary

shapiro.test(foldtouch_comfort$rating)

foldtouch_comfort$id = factor(foldtouch_comfort$id)
foldtouch_comfort$locationY = factor(foldtouch_comfort$locationY)


m <- art(
  rating ~ angle_code*locationX_code*locationY + (1|id),
  data = foldtouch_comfort
)

anova(m)

art.con(m, "locationX_code:locationY")
art.con(m, "locationY")

```

#### Confidence
```{r warning=FALSE}


foldtouch_confidence <- foldtouch_trials %>%
  filter(category == "confidence")

participants_foldtouch_confidence <- full_join(foldtouch_confidence, participants)

boxplot(rating~gesture_code,data=foldtouch_confidence, main="Confidence",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


foldtouch_confidence_summary <-foldtouch_confidence %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_confidence_summary

# line + dot
confidence_graph <- ggplot(foldtouch_confidence_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#EB984E", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

confidence_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("confidence_foldtouch.pdf", width = 4, height = 4)

# foldtouch_confidence_angle_summary <-foldtouch_confidence %>%
#   group_by(angle_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# confidence_graph <- ggplot(foldtouch_confidence_angle_summary) +
#   geom_pointrange( aes(x=angle_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#c0392b", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# confidence_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("confidence_foldtouch_angle.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

foldtouch_data_summary <-foldtouch_confidence %>%
  group_by(angle_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_data_summary

foldtouch_angle_summary <-foldtouch_confidence %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_angle_summary


foldtouch_X_summary <-foldtouch_confidence %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_X_summary

foldtouch_Y_summary <-foldtouch_confidence %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_Y_summary

shapiro.test(foldtouch_confidence$rating)

foldtouch_confidence$id = factor(foldtouch_confidence$id)
foldtouch_confidence$locationY = factor(foldtouch_confidence$locationY)

m <- art(
  rating ~ angle_code*locationX_code*locationY + (1|id),
  data = foldtouch_confidence
)

anova(m)

art.con(m, "locationY")

```

#### Social acceptance
```{r warning=FALSE}


foldtouch_social <- foldtouch_trials %>%
  filter(category == "social")

participants_foldtouch_social <- full_join(foldtouch_social, participants)

boxplot(rating~gesture_code,data=foldtouch_social, main="Social",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


foldtouch_social_summary <-foldtouch_social %>%
  group_by(gesture_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_social_summary

# line + dot
social_graph <- ggplot(foldtouch_social_summary) +
  geom_pointrange( aes(x=reorder(gesture_code, desc(gesture_code)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#A569BD", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

social_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("social_foldtouch.pdf", width = 4, height = 4)
# 
# foldtouch_social_angle_summary <-foldtouch_social %>%
#   group_by(angle_code) %>%
#   summarize(
#     meanScore = rating %>% mean(na.rm=TRUE),
#     lowCI = ci(rating)[2]%>% pmax(0),
#     highCI = ci(rating)[3]%>% pmin(7),
#     sd = ci(rating)[4],
#     std = rating %>% sd())
# 
# # line + dot
# social_graph <- ggplot(foldtouch_social_angle_summary) +
#   geom_pointrange( aes(x=angle_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#5d6d7e", alpha=0.9, size=0.8) +
#   scale_y_reverse(lim=c(7,2)) + 
#   coord_flip()
# 
# social_graph + theme( # remove the vertical grid lines
#           panel.background = element_blank(),
#           panel.grid.major.y = element_blank() ,
#           # explicitly set the horizontal lines (or they will disappear too)
#           panel.grid.major.x = element_line( size=.1, color="gray" ),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           axis.text.y=element_blank()
#     )
# 
# ggsave("social_foldtouch_angle.pdf", width = 4, height = 1)


```
#### analysis

```{r warning=FALSE}

foldtouch_data_summary <-foldtouch_social %>%
  group_by(angle_code, locationX_code, locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_data_summary

foldtouch_angle_summary <-foldtouch_social %>%
  group_by(angle_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_angle_summary


foldtouch_X_summary <-foldtouch_social %>%
  group_by(locationX_code) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_X_summary

foldtouch_Y_summary <-foldtouch_social %>%
  group_by(locationY) %>%
  summarize(
    meanScore = rating %>% mean(na.rm=TRUE),
    lowCI = ci(rating)[2]%>% pmax(0),
    highCI = ci(rating)[3]%>% pmin(7),
    sd = ci(rating)[4],
    std = rating %>% sd())

foldtouch_Y_summary

shapiro.test(foldtouch_social$rating)

foldtouch_social$id = factor(foldtouch_social$id)
foldtouch_social$locationY = factor(foldtouch_social$locationY)

m <- art(
  rating ~ angle_code*locationX_code*locationY + (1|id),
  data = foldtouch_social
)

anova(m)

art.con(m, "locationY")

```


### interaction


#### Ease
```{r warning=FALSE}


data_ease <- data %>%
  filter(category == "easiness")

boxplot(rating~type_code,data=data_ease, main="Ease",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


rating_data <- data_ease %>%
  group_by(id, type_code) %>%
  summarize(
    rating_ave = sum(rating) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id,  type_code)

rating_data

ease_summary <-rating_data %>%
  group_by(type_code) %>%
  summarize(
    meanScore = rating_ave %>% mean(na.rm=TRUE),
    lowCI = ci(rating_ave)[2]%>% pmax(0),
    highCI = ci(rating_ave)[3]%>% pmin(7),
    sd = ci(rating_ave)[4],
    std = rating_ave %>% sd())

ease_summary

# line + dot
ease_graph <- ggplot(ease_summary) +
  geom_pointrange( aes(x=type_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

ease_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("ease_type.pdf", width = 4, height = 1.5)



```
#### analysis

```{r warning=FALSE}


shapiro.test(rating_data$rating_ave)

#library(ez) # for ezANOVA
#rating_data$id= factor(rating_data$id) # Subjectid must be nominal
#ezANOVA(rating_data, dv=.(rating_ave), wid=.(id), within=.(type_code))

#pairwise.t.test(rating_data$rating_ave, rating_data$type_code, p.adjust="bonf")

library(coin)
rating_data$id= factor(rating_data$id) # Subjectid must be nominal
friedman_test(rating_ave~ type_code | id, data=rating_data, distribution="asymptotic")

library(reshape2) # for dcast
rating_data2 <-dcast(rating_data, id ~ type_code, value.var="rating_ave") # make wide-format table
ab = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$TOUCHFOLD, paired=TRUE) # a vs. b
ac = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$FOLD, paired=TRUE) # a vs. c
bc= wilcox.test(rating_data2$TOUCHFOLD, rating_data2$FOLD, paired=TRUE) # b vs. c
p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

```


#### Comfort
```{r warning=FALSE}


comfort_data <- data %>%
  filter(category == "comfort")

boxplot(rating~type_code,data=comfort_data, main="Comfort",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)

rating_data <- comfort_data %>%
  group_by(id, type_code) %>%
  summarize(
    rating_ave = sum(rating) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id,  type_code)

rating_data


comfort_summary <-rating_data %>%
  group_by(type_code) %>%
  summarize(
    meanScore = rating_ave %>% mean(na.rm=TRUE),
    lowCI = ci(rating_ave)[2]%>% pmax(0),
    highCI = ci(rating_ave)[3]%>% pmin(7),
    sd = ci(rating_ave)[4],
    std = rating_ave %>% sd())

comfort_summary

# line + dot
comfort_graph <- ggplot(comfort_summary) +
  geom_pointrange( aes(x=type_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

comfort_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("comfort_type.pdf", width = 4, height = 1.5)


```
#### analysis

```{r warning=FALSE}



shapiro.test(rating_data$rating_ave)

#library(ez) # for ezANOVA
#rating_data$id= factor(rating_data$id) # Subjectid must be nominal
#ezANOVA(rating_data, dv=.(rating_ave), wid=.(id), within=.(type_code))

#pairwise.t.test(rating_data$rating_ave, rating_data$type_code, p.adjust="bonf")

library(coin)
rating_data$id= factor(rating_data$id) # Subjectid must be nominal
friedman_test(rating_ave~ type_code | id, data=rating_data, distribution="asymptotic")

library(reshape2) # for dcast
rating_data2 <-dcast(rating_data, id ~ type_code, value.var="rating_ave") # make wide-format table
ab = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$TOUCHFOLD, paired=TRUE) # a vs. b
ac = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$FOLD, paired=TRUE) # a vs. c
bc= wilcox.test(rating_data2$TOUCHFOLD, rating_data2$FOLD, paired=TRUE) # b vs. c
p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")



```

#### Confidence
```{r warning=FALSE}


confidence_data <- data %>%
  filter(category == "confidence")

boxplot(rating~type_code,data=confidence_data, main="Confidence",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)


rating_data <- confidence_data %>%
  group_by(id, type_code) %>%
  summarize(
    rating_ave = sum(rating) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id,  type_code)

rating_data


confidence_summary <-rating_data %>%
  group_by(type_code) %>%
  summarize(
    meanScore = rating_ave %>% mean(na.rm=TRUE),
    lowCI = ci(rating_ave)[2]%>% pmax(0),
    highCI = ci(rating_ave)[3]%>% pmin(7),
    sd = ci(rating_ave)[4],
    std = rating_ave %>% sd())

confidence_summary

# line + dot
confidence_graph <- ggplot(confidence_summary) +
  geom_pointrange( aes(x=type_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#EB984E", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

confidence_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("confidence_type.pdf", width = 4, height = 1.5)



```
#### analysis

```{r warning=FALSE}



shapiro.test(rating_data$rating_ave)

#library(ez) # for ezANOVA
#rating_data$id= factor(rating_data$id) # Subjectid must be nominal
#ezANOVA(rating_data, dv=.(rating_ave), wid=.(id), within=.(type_code))

#pairwise.t.test(rating_data$rating_ave, rating_data$type_code, p.adjust="bonf")

library(coin)
rating_data$id= factor(rating_data$id) # Subjectid must be nominal
friedman_test(rating_ave~ type_code | id, data=rating_data, distribution="asymptotic")

library(reshape2) # for dcast
rating_data2 <-dcast(rating_data, id ~ type_code, value.var="rating_ave") # make wide-format table
ab = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$TOUCHFOLD, paired=TRUE) # a vs. b
ac = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$FOLD, paired=TRUE) # a vs. c
bc= wilcox.test(rating_data2$TOUCHFOLD, rating_data2$FOLD, paired=TRUE) # b vs. c
p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")


```

#### Social acceptance
```{r warning=FALSE}


social_data <- data %>%
  filter(category == "social")

boxplot(rating~type_code,data=social_data, main="Social",
   xlab="Gesture", ylab="likert scale", horizontal=TRUE, outline = FALSE)

rating_data <- social_data %>%
  group_by(id, type_code) %>%
  summarize(
    rating_ave = sum(rating) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id,  type_code)

rating_data

social_summary <-rating_data %>%
  group_by(type_code) %>%
  summarize(
    meanScore = rating_ave %>% mean(na.rm=TRUE),
    lowCI = ci(rating_ave)[2]%>% pmax(0),
    highCI = ci(rating_ave)[3]%>% pmin(7),
    sd = ci(rating_ave)[4],
    std = rating_ave %>% sd())

social_summary

# line + dot
social_graph <- ggplot(social_summary) +
  geom_pointrange( aes(x=type_code, y=meanScore, ymin=lowCI, ymax=highCI), colour="#A569BD", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,2)) + 
  coord_flip()

social_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("social_type.pdf", width = 4, height = 1.5)



```
#### analysis

```{r warning=FALSE}




shapiro.test(rating_data$rating_ave)

#library(ez) # for ezANOVA
#rating_data$id= factor(rating_data$id) # Subjectid must be nominal
#ezANOVA(rating_data, dv=.(rating_ave), wid=.(id), within=.(type_code))

#pairwise.t.test(rating_data$rating_ave, rating_data$type_code, p.adjust="bonf")

library(coin)
rating_data$id= factor(rating_data$id) # Subjectid must be nominal
friedman_test(rating_ave~ type_code | id, data=rating_data, distribution="asymptotic")

library(reshape2) # for dcast
rating_data2 <-dcast(rating_data, id ~ type_code, value.var="rating_ave") # make wide-format table
ab = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$TOUCHFOLD, paired=TRUE) # a vs. b
ac = wilcox.test(rating_data2$FOLDTOUCH, rating_data2$FOLD, paired=TRUE) # a vs. c
bc= wilcox.test(rating_data2$TOUCHFOLD, rating_data2$FOLD, paired=TRUE) # b vs. c
p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")



```

### correlation

```{r warning=FALSE}

library("ggpubr")
res <- cor.test(participants_fold_ease$rating, participants_fold_ease$handLength, 
                    method = "spearman")
res

ggscatter(participants_fold_ease, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_fold_ease$rating, participants_fold_ease$handWidth, 
                    method = "spearman")
res

ggscatter(participants_fold_ease, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_fold_comfort$rating, participants_fold_comfort$handLength, 
                    method = "spearman")
res

ggscatter(participants_fold_comfort, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_fold_comfort$rating, participants_fold_comfort$handWidth, 
                    method = "spearman")
res

ggscatter(participants_fold_comfort, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_fold_social$rating, participants_fold_social$handLength, 
                    method = "spearman")
res

ggscatter(participants_fold_social, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_fold_social$rating, participants_fold_social$handWidth, 
                    method = "spearman")
res

ggscatter(participants_fold_social, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_fold_confidence$rating, participants_fold_confidence$handLength, 
                    method = "spearman")
res

ggscatter(participants_fold_confidence, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_fold_confidence$rating, participants_fold_confidence$handWidth, 
                    method = "spearman")
res

ggscatter(participants_fold_confidence, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")
```

```{r warning=FALSE}

library("ggpubr")
res <- cor.test(participants_touchfold_ease$rating, participants_touchfold_ease$handLength, 
                    method = "spearman")
res

ggscatter(participants_touchfold_ease, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_touchfold_ease$rating, participants_touchfold_ease$handWidth, 
                    method = "spearman")
res

ggscatter(participants_touchfold_ease, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_touchfold_comfort$rating, participants_touchfold_comfort$handLength, 
                    method = "spearman")
res

ggscatter(participants_touchfold_comfort, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_touchfold_comfort$rating, participants_touchfold_comfort$handWidth, 
                    method = "spearman")
res

ggscatter(participants_touchfold_comfort, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_touchfold_social$rating, participants_touchfold_social$handLength, 
                    method = "spearman")
res

ggscatter(participants_touchfold_social, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_touchfold_social$rating, participants_touchfold_social$handWidth, 
                    method = "spearman")
res

ggscatter(participants_touchfold_social, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_touchfold_confidence$rating, participants_touchfold_confidence$handLength, 
                    method = "spearman")
res

ggscatter(participants_touchfold_confidence, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_touchfold_confidence$rating, participants_touchfold_confidence$handWidth, 
                    method = "spearman")
res

ggscatter(participants_touchfold_confidence, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")
```

```{r warning=FALSE}

library("ggpubr")
res <- cor.test(participants_foldtouch_ease$rating, participants_foldtouch_ease$handLength, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_ease, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_foldtouch_ease$rating, participants_foldtouch_ease$handWidth, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_ease, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_foldtouch_comfort$rating, participants_foldtouch_comfort$handLength, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_comfort, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_foldtouch_comfort$rating, participants_foldtouch_comfort$handWidth, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_comfort, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_foldtouch_social$rating, participants_foldtouch_social$handLength, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_social, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_foldtouch_social$rating, participants_foldtouch_social$handWidth, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_social, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")

res <- cor.test(participants_foldtouch_confidence$rating, participants_foldtouch_confidence$handLength, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_confidence, x = "handLength", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handLength", ylab = "rating")

res <- cor.test(participants_foldtouch_confidence$rating, participants_foldtouch_confidence$handWidth, 
                    method = "spearman")
res

ggscatter(participants_foldtouch_confidence, x = "handWidth", y = "rating", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "handWidth", ylab = "rating")
```